Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-12 paper/ijcai/paper.tex
small fix
pass on abstract

\begin{abstract}
  The task of locating faulty code from failing testing is a very
  important problem known as software fault localization. This paper
  reports on a comprehensive study to reassess the impact of combining
  two very popular techniques to that end--Dynamic Slicing and
  Spectrum-based Fault Localization. Our results show that \Fix{...}
\end{abstract}

>>>>

\begin{abstract}
  Software debugging is important and challenging. This paper reports
  on a comprehensive study to reassess the impact of combining two
  very popular automated techniques for software fault
  localization--Dynamic Slicing and Spectrum-based Fault
  Localization. Our results show that \Fix{...}
\end{abstract}
